### 2021-07-21 paper/paper.tex
add MPI.jl reference

@@

TODO: Andrew, please describe the setups that you used.

@@

>>>>

\section{Design of Trixi.jl and feature overview}

TODO %TODO

@@

TODO: Andrew, please describe the setups that you used. %TODO

@@

\section{Assessment of Julia for simulation-focused scientific computing}

TODO %TODO
\begin{itemize}
  \item Some nice features
  \item Compilation time can be annoying but also allows cool features and performance
  \item Extendability: Multi-physics with 350 lines of code \cite{schlottkelakemper2021purely}
  \item MPI: To be evaluated but the basic tools are already there \cite{byrne2021mpi}
\end{itemize}

\section{Summary and conclusions}

TODO %TODO

\section*{Acknowledgments}

Funded by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation)
under Germany's Excellence Strategy EXC 2044-390685587, Mathematics Münster:
Dynamics-Geometry-Structure.

TODO %TODO
